\pkg{ggenealogy}: An \proglang{R} Package for Visualizing Genealogical Data

### 2016-03-05 JSS/jss-style/article.tex
MGP graphic

\section{Demonstration Dataset}

The available data used in the current demonstration of the software is a data frame structure that contains 412 rows, each representing a direct parent-child relationship between a pair of soybean varieties. In total, there are 230 unique soybean varieties present. These data were collected from field trials, genetic studies, and United States Department of Agriculture (USDA) bulletins, and date as early as the first decade of the 1900s. They also contain information on the developmental years, as well as the copy number variants, single nucleotide polymorphisms, protein content, and yield, of each of the soybeans.

@@

@@

@@

\bibliography{foo}

>>>>

\section{Soybean Genealogy Dataset}

The \proglang{ggenealogy} package comes with two example datasets, one comprises a soybean genealogy and the other comprises an academic statistician genealogy. We will introduce both example datasets in this paper to demonstrate some of the tools available in the software. We start with the soybean genealogy, which is available in a data frame structure with 412 rows, each representing a direct parent-child relationship between a pair of soybean varieties. In total, there are 230 unique soybean varieties in the dataset. These data were collected from field trials, genetic studies, and United States Department of Agriculture (USDA) bulletins, and date as early as the first decade of the 1900s. They also contain information on the developmental years, as well as the copy number variants, single nucleotide polymorphisms, protein content, and yield, of each of the soybeans.

@@

\section{Academic Genealogy of Statisticians Dataset}

In addition to the soybean genealogy, the \proglang{ggenealogy} package also comes with an academic genealogy of statisticians. To develop this later dataset, we contacted the Mathematics Genealogy Project, a web-based database for the genealogy of academic mathematicians. This database, which currently contains almost 200,000 entries, is a service of the North Dakota State University Department of Mathematics and the American Mathematical Society. The Mathematics Genealogy Project contact provided us a Structured Query Language (SQL) export, and we used PostgreSQL to query the database (\citealt{psql}, \citealt{sql}).

Each entry in the database contained 26 variables pertaining to an individual who received a graduate-level academic degree in statistics. One of these variables was called ``msc" (Mathematics Subject Classification), and we selected only those entries that contained a value of 62 for this variable (coded as ``Statistics"). This process resulted in 8995 entries, which we further reduced by only retaining those entries that contained an advisor who was also in the field ``Statistics". For each of the remaining 3293 entries, we only maintained 6 of the variables. This process resulted in the second example dataset provided in the \proglang{ggenealogy} package

This later example dataset is available in a data frame structure that contains 3293 rows, each which corresponds to a parent-child relationship, where the child is an individual who received a graduate-level academic degree in statistics. The parent is the advisor

\begin{CodeChunk}
\begin{CodeInput}
R> data(statGeneal)
R> dim(statGeneal)
\end{CodeInput}
\begin{CodeOutput}
[1] 3293    6
\end{CodeOutput}
\begin{CodeInput}
R> colnames(statGeneal)
\end{CodeInput}
\begin{CodeOutput}
[1] "child"   "parent"  "year"    "country" "school"  "thesis"
\end{CodeOutput}
\end{CodeChunk}

which is available in a data frame structure with 412 rows, each representing a direct parent-child relationship between a pair of soybean varieties. In total, there are 230 unique soybean varieties in the dataset. These data were collected from field trials, genetic studies, and United States Department of Agriculture (USDA) bulletins, and date as early as the first decade of the 1900s. They also contain information on the developmental years, as well as the copy number variants, single nucleotide polymorphisms, protein content, and yield, of each of the soybeans.

@@

\begin{figure}%[h]
    \centering
    \includegraphics[width=\textwidth]{dCox.png}
    \caption{plot7}
    \label{fig:dCox}
\end{figure}

@@

\bibliography{article}
